Accessing the nucleon tensor structure in inclusive deep inelastic scattering

### 2016-07-26 1607 - JMC for g2/Paper/JMC_dis.tex
worked on BC discussion

\author{Alberto~Accardi$^{a}$, Alessandro~Bacchetta$^{b}$} 
\affiliation{
$^a$Jefferson Lab, Newport News, VA 23606, USA, and
Hampton University, Hampton, VA 23668, USA \\
$^b$Dipartimento di Fisica, Universit\`a degli Studi di Pavia, and INFN,
Sez. di Pavia, 27100 Pavia, Italy
}

@@

\begin{abstract}

\end{abstract}

@@

It is important to notice that $\xi_2=1$ exactly due to CPT invariance \cite{Weinberg-book}, while $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is dynamically determined. From the analytic properties of spectral functions we may expect \cite{Accardi:2008ne} $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2 (\mu^2) \theta (\mu^2-m_\pi^2)$ with the continuum starting at $m_\pi$, the mass of the pion, due to color confinement effects. Taking into account that $J_1 < J_2$, we may therefore expect 

@@

Rather than directly using the definition \eqref{e:xi_A}, it is convenient to calculate the inclusive cross section as an integral of the semi-inclusive one, utilize the QCD equation of motions and furthermore summed over all hadron flavors, and take advantage of 
\begin{align}
  \label{eq:SIDIS_to_DIS}
  \sum_h \int \frac{d^3p_h}{(2\pi)2E_h} \Delta^h(l,p_h) = \Xi(l) \ , 
\end{align}
where $\Delta^h$ is the quark fragmentation correlator for production of a hadron of flavor $h$ and momentum $p_h$ \cite{Bacchetta:2006tn}. In terms of the TMD fragmentation functions we are interested in, this reads
\begin{align}
  \label{eq:SIDIS_to_DIS_TMDlevel}
  \sum_h \int dz d^2p_{hT} z D_1^h(z,p_{hT}) & = \xi_2 = 1   \\
  \sum_h \int dz d^2p_{hT} E(z,p_{hT}) & = \xi_1 \ ,
\end{align}
where $D_1^h(z,p_{hT})$ is the twist-2 quark fragmentation function as a function of the hadron's collinear momentum fraction $z$ and transverse momentum $p_{hT}$, and $\tilde E^h(z,p_{hT})$ is a chiral-odd twist-3 function defined in \cite{Bacchetta:2006tn}.

% As we shall see, an analogous formula for quark-gluon-quark correlators is not needed.
%The $\xi_1$ term is chiral-odd and therefore can appear in the inclusive cross section only coupled to the transversity function $h_1$. Therefore, for our analysis 
The relevant part of the semi-inclusive hadronic tensor for our analysis is 
\todo{[AA] I am using the notation in Piet Mulder's lecture notes - this will need to be checked.}
\begin{align}
  \label{eq:Wsidis_ini}
  2 \Lambda  W^{\mu\nu}
    & = i \frac{2\Lambda}{Q} \hat t^{[\mu}_{\phantom \perp} 
    \epsilon_\perp^{\nu]\rho}S_{\perp\rho} 
    \sum_q e_q^2
    \bigg[ 2 x_b g_T(x_B) \sum_h \int dz d^2p_{hT} D_1^{q,h}(z,p_{hT}) 
  %\\ &
  + 2 h_1(x_B) \sum_h \int dz d^2p_{hT} \tilde E^{q,h}(z,p_{hT}) \bigg] + \ldots
\end{align}
Here and we reintroduced the quark flavor $q$ for maximum clarity, and $e_q$ its electric charge.
The first term can be easily integrated with the help of the sum rule \eqref{eq:SIDIS_to_DIS_TMDlevel}. To integrate the latter, we first need make use of the relation $\tilde E(z) = E(z) - (\mq/\Lambda) z D_1(z)$, which is a consequence of the QCD equations of motion \cite{Bacchetta:2006tn}, then utilize the sum rule \eqref{eq:SIDIS_to_DIS}:
\begin{align}
  \sum_h \int dz d^2p_{hT} \tilde E^{q,h}(z,p_{hT}) 
    = \sum_h \int dz d^2p_{hT} \Big[ E^{q,h}(z,p_{hT}) - \frac{\mq}{\Lambda} z D_1^{q,h}(z,p_{hT}) \Big]
    = \xi_1 - \frac{\mq}{\Lambda} \xi_2 = \frac{\mj - \mq}{\Lambda} \ .
\end{align}
This formula is the single most important result of this paper, and provides a
non perturbative generalization of the commonly used $\int\tilde E =0$ sum
rule introduced in \cite{Jaffe:1996zw}. Indeed, calculating the jet correlator 
on the perturbative vacuum one would obtain, as already discussed, $\mj=\mq$
and the new term would vanish.

@@

The first term is also known as the Wandzura-Wilczeck function $g_2^{WW} =
g_1^*(x)$ , and contains all the ``pure twist-2'' chiral even contributions to
the $g_2$ structure coming from quark-quark correlators. The second and third
terms contain all ``pure twist-3'' contributions, i.e., those coming from
quark-gluon-quark correlators. The fourth and fifth terms depend on the
transversity parton distribution function, $h_1$. 
The former is usually neglected for
light quarks since it is proportional to $\mq=O$(1 MeV). In the latter term,
new in our analysis, the transversity distribution is multiplied by a constant
of $O$(100 MeV), and cannot be a priori neglected.

It is important to estimate the size of teh variou scontributions to the non Wandzura-Wilczek part of $g_2$. We define the shorthand notation
\begin{align}
g_2^{tw3} & = \frac{1}{2}\,\sum_a e_a^2
    \biggl(
    \widetilde g_T^{a \star}(x) 
    + \int_x^1\frac{dy}{y} \widehat{g}_T^q(y) 
    \biggr) 
&
g_2^{\text{quark}} &= \frac{1}{2}\,\sum_a e_a^2 
 \frac{\mq}{\Lambda} (h_1^q/x)^\star(x),
&
g_2^{\text{jet}} &= \frac{1}{2}\,\sum_a e_a^2 
\frac{\mj-\mq}{\Lambda} \frac{h_1^q(x)}{x}. 
\end{align} 
These are comapred in Figure~\ref{f:g2contrib} to the $g_2-g_2^{WW}$ function
obtained in the very recent JAM15 fit of polarized DIS asymmetries
\cite{Sato:2016tuz}, that includes a large amount of precise data at large $x$
from Jefferson Lab, and simultaneously fits the higher-twist components of in
$g_1$ and $g_2$ to the data. For the ``pure twist-3'' contribution,
$g_2^{tw3}$, {\it i.e.}, the contribution from quark-gluon-quark matrix
elements, we show a model calculation by Braun et al. \cite{Braun-et-al}; for
other estimates, see \cite{Other-tw3-calcs}. To estimate the contributions
from quark ($g_2^q$) and jet mass ($g_2^{jet}$) effects, that depend on chiral
odd quark-quark matrix elements, we use the recent Pavia15 fit of the
transversity distribution from Ref.~\cite{Radici:2015mwa}, which is comparable
also to other 
extractions~\cite{Anselmino:2013vqa,Kang:2015msa}. Furthermore, we choose the
values of the mass parameters to be $\mq=5$ MeV and $\mj = 100$ MeV.

@@

\begin{itemize}
\item smaller-$x$: constrains the small-$x$ behavior of transversity.
\end{itemize}
Some ideas to check:
\begin{itemize}
\item JAM13 neutron has almost 0 twist 3, with small positive contribution at small x. Can we use this to highlight teh $g_2^{jet}$ contribution? Or maybe as a cnstrain: if Braun is right then $g_2^{jet}(n) \approx -g_2^{tw3}(n)$. (still, does not help much for the proton).
\item In Jam 13, Fig. 6, it looks like in general the violation of the BC sum rule is a small-x effect --> constraints on h(x) fits? This cannot really be checked vs. JAM15, that assumes $g_2^(0)$ respects BC. 
\end{itemize}

\begin{figure}[tbh]
\begin{center}
\includegraphics[width=8cm]{g2contrib}
\includegraphics[width=8cm]{g2contribN}
\caption{\label{f:g2contrib} 
Different contributions to the non Wandzura-Wilczek part of the proton (left)
and neutron (right) $g_2$ structure function compared to the JAM15 fit of the
$g_2-g_2^{\text{WW}}$ (solid black) \cite{Sato:2016tuz}. The quark and jet
contributions are shown with a dotted red and a dot-dashed green line
respectively, with uncertainty bands coming form the Pavia15 fit of the
transversity function \cite{Radici:2015mwa}. The unceratainty in the choice
$m_q=5$ GeV and $M_q=100$ GeV is not shown. The pure twist-3 contribution
calculated by Braun et al. \cite{Braun:2011aw} is shown as a dashed blue line
(no uncertainty estiamte was provided in teh original reference). 
}
\end{center}
\end{figure}

It is interesting to consider the moments of the non Wandzura-Wilczek contribution to $g-2$,
\begin{align}
  d_N = N \int_0^1 x^N \big( g_2(x) - g_2^{WW}(x) \big) \ .
\end{align}
For a generic function $f$, let us define it's $N$-th moment as $f[N]=\int_0^1 dx\, x^{N} f(x)$. It is then straightforward to verify that $f^*[N] = N/(N+1) f[N]$ and  
\begin{align}
  d_N & \equiv (N+1) g_2[N] + N g_1[N] \\
  & = \frac12 \sum_q e_q^2 \bigg( N \tilde g_T^q[N] + \hat g_T^q[N]
    + \frac{(N+1) M_q-m_q}{\Lambda} h_1^q[N] \bigg) \ .
\end{align}
\AAcom{The notation used in JAM15 with $x^{N-1}$ for the Nth moment is pretty awkward here. Should we use $x^N$ instead?}

The zero-th moment corresponds to an extension of teh Burkhardt-Cottingham sum rule \cite{Burkhardt:1970ti,Jaffe:1996zw}, that appears to be broken by the non-perturbative spin-flip contribution from the jet function: 
\begin{align}
  \label{eq:BC}
  \int dx\, g_2(x) = \frac{\mj-\mq}{\Lambda} \int dx\, \frac{1}{x} h_1(x) \ .
\end{align}
This sum rule, in which the pure twist-3 part does not take part, is a consequence of the Lorentz invariance of the DIS cross section, that entails $\int_0^1 dx g_1^a(x) = \int_0^1 g_T^q(x)$. It explicitly displays a contribution from spin-flip processes, that are included in the original derivation by Burkhardt and Cottingham \cite{Burkhardt:1970ti} but do not show up in treatments that only consider free field quark propagators for the struck quark \cite{Jaffe:1996zw}.

Assuming the Burkhardt-Cottingham sum rule to be strictly valid, we obtain a strong constraint on the transversity function,
\begin{align}
   \int dx\, \frac{1}{x} h_1(x) = 0 \ .
\label{eq:ABsumrule}
\end{align}
Even if the BC sun rule is broken by a 
$J = 0$ fixed pole with non-polynomial residue, i.e., if $g_2$ integrates to a finite but non-zero number \cite{Jaffe:1996zw}), we obtain that $h_1(x)/x$ must be integrable. This entails a bound on the small $x$ behavior of the transversity,
\begin{align}
  h_1(x) \propto x^\epsilon \ \ \ \epsilon>0 \ .
\label{eq:ABbound}
\end{align}
This bound will be very useful, \eg, in transversity fits, where the data at small $x$ is, as yet, very limited, and in general for proper extrapolations when calculating moments.

The first moment is the first in which a contribution from the pure twist-3 part of $g_2$ appears:
\begin{align}
  d_1 & = \frac12 \sum_q e_q^2 \bigg( 2 \tilde g_T^q[1] + \hat g_T^q[1]
    + \frac{2M_q-m_q}{\Lambda} h_1^q[1] \bigg)
\end{align}
where $h_1^q[1] = \int_0^1 \dx $ is the contribution of a quark $q$ to the tensor charge. In this case, the transevrsity contribution is a background to the extraction of teh poure twist-3 piece. Fortunately, it is a quantity that can be extracted from the lattice \cite{Bhattacharya:2016zcn} or fitted \cite{Pavia15, others, reviews?}. Furthermore the new sum rule \eqref{eq:ABsumrule} and bound \eqref{eq:ABbound} promise to improve future transversity fits. What is less obvious is how to calculate $M_q-m_q$ from first principles, since this is related to the spectral function of the quark propagator. We will, however, discuss later perspectives on how to measure it. Therefore the pure twist-3 part can, in principle, be properly isolated.

The third moment is interesting because the pure twist-3 part can be related to quark-gluon-quark correlators, see \cite{Jaffe-lectures}, and interpreted as as the average color force experienced by the struck quark as it exits teh nucleon \cite{M.Burkardt}. As in the previous case, however, the transversity contribution needs to be subtracted:
\begin{align}
  d_2 & = \frac12 \sum_q e_q^2 \bigg( 3 \tilde g_T^q[2] + \hat g_T^q[2]
    + \frac{3M_q-m_q}{\Lambda} h_1^q[2] \bigg)
\end{align}

>>>>

\author{Alberto~Accardi$^{a}$, Alessandro~Bacchetta$^{b}$} 
\affiliation{
$^a$Hampton University, Hampton, VA 23668, USA,
and Jefferson Lab, Newport News, VA 23606, USA \\
$^b$Dipartimento di Fisica, Universit\`a degli Studi di Pavia, and INFN,
Sez. di Pavia, 27100 Pavia, Italy
}

@@

\begin{abstract}
We revisit the standard analysis of inclusive DIS on protons taking into account the fact that on-shell quarks cannot be present in the final state, but they rather decay into hadrons. As a consequence, a spin-flip term associated with the invariant mass of this (mini)jet of hadrons is generated non perturbatively, and couples to the target's transversity distribution function. In inclusive cross sections, this provides an hitherto neglected and large contribution to the twist-3 part of the $g_2$ structure function, that can explain the discrepancy between recent calculations and fits of this quantity. It also provides an extension of the Burkardt-Cottingham sum rule, that puts stringent constraints on the small-$x$ behavior of the transversity function. Perspectives to measure the new spin flip term, and applications to spin-1 targets will be briefly discussed.
\end{abstract}

@@

It is important to notice that $\xi_2=1$ exactly due to CPT invariance \cite{Weinberg-book}, while $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is dynamically determined. From the analytic properties of spectral functions we may expect \cite{Accardi:2008ne)} $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2 (\mu^2) \theta (\mu^2-m_\pi^2)$ with the continuum starting at $m_\pi$, the mass of the pion, due to color confinement effects. Taking into account that $J_1 < J_2$, we may therefore expect 

@@

Rather than directly using the definition \eqref{e:xi_A}, it is convenient to calculate the inclusive cross section as an integral of the semi-inclusive one, utilize the QCD equation of motions and furthermore summed over all hadron flavors, and take advantage of 
\begin{align}
  \label{eq:SIDIS_to_DIS}
  \sum_h \int \frac{d^3p_h}{(2\pi)2E_h} \Delta^h(l,p_h) = \Xi(l) \ , 
\end{align}
where $\Delta^h$ is the quark fragmentation correlator for production of a hadron of flavor $h$ and momentum $p_h$ \cite{New_testament}. In terms of the TMD fragmentation functions we are interested in, this reads
\begin{align}
  \label{eq:SIDIS_to_DIS_TMDlevel}
  \sum_h \int dz d^2p_{hT} z D_1^h(z,p_{hT}) & = \xi_2 = 1   \\
  \sum_h \int dz d^2p_{hT} E(z,p_{hT}) & = \xi_1 \ ,
\end{align}
where $D_1^h(z,p_{hT})$ is the twist-2 quark fragmentation function as a function of the hadron's collinear momentum fraction $z$ and transverse momentum $p_{hT}$, and $\tilde E^h(z,p_{hT})$ is a chiral-odd twist-3 function defined in \cite{New-testament}.

% As we shall see, an analogous formula for quark-gluon-quark correlators is not needed.
%The $\xi_1$ term is chiral-odd and therefore can appear in the inclusive cross section only coupled to the transversity function $h_1$. Therefore, for our analysis 
The relevant part of the semi-inclusive hadronic tensor for our analysis is 
\todo{[AA] I am using the notation in Piet Mulder's lecture notes - this will need to be checked.}
\begin{align}
  \label{eq:Wsidis_ini}
  2 \Lambda  W^{\mu\nu}
    & = i \frac{2\Lambda}{Q} \hat t^{[\mu}_{\phantom \perp} 
    \epsilon_\perp^{\nu]\rho}S_{\perp\rho} 
    \sum_q e_q^2
    \bigg[ 2 x_b g_T(x_B) \sum_h \int dz d^2p_{hT} D_1^{q,h}(z,p_{hT}) 
  %\\ &
  + 2 h_1(x_B) \sum_h \int dz d^2p_{hT} \tilde E^{q,h}(z,p_{hT}) \bigg] + \ldots
\end{align}
Here and we reintroduced the quark flavor $q$ for maximum clarity, and $e_q$ its electric charge.
The first term can be easily integrated with the help of the sum rule \eqref{eq:SIDIS_to_DIS_TMDlevel}. To integrate the latter, we first need make use of the relation $\tilde E(z) = E(z) - (\mq/\Lambda) z D_1(z)$, which is a consequence of the QCD equations of motion \cite{New-testament}, then utilize the sum rule \eqref{eq:SIDIS_to_DIS}:
\begin{align}
  \sum_h \int dz d^2p_{hT} \tilde E^{q,h}(z,p_{hT}) 
    = \sum_h \int dz d^2p_{hT} \Big[ E^{q,h}(z,p_{hT}) - \frac{\mq}{\Lambda} z D_1^{q,h}(z,p_{hT}) \Big]
    = \xi_1 - \frac{\mq}{\Lambda} \xi_2 = \frac{\mj - \mq}{\Lambda} \ .
\end{align}
This formula is the single most important result of this paper, and provides a non perturbative generalization of the commonly used $\int\tilde E =0$ sum rule introduced in \cite{Jaffe-Ji}. Indeed, calculating the jet correlator
on the perturbative vacuum one would obtain, as already discussed, $\mj=\mq$
and the new term would vanish.

@@

The first term is also known as the Wandzura-Wilczeck function $g_2^{WW} =
-g_1^*(x)$ , and contains all the ``pure twist-2'' chiral even contributions to
the $g_2$ structure coming from quark-quark correlators. The second and third
terms contain all ``pure twist-3'' contributions, i.e., those coming from
quark-gluon-quark correlators. The fourth and fifth terms depend on the
transversity parton distribution function, $h_1$. 
The fourth term is usually neglected for
light quarks since it is proportional to $\mq=O$(1 MeV). In the last term,
new in our analysis, the transversity distribution is multiplied by a constant
of $O$(100 MeV), and cannot be a priori neglected.

It is important to estimate the size of the various contributions to the non Wandzura-Wilczek part of $g_2$. We define the shorthand notation
\begin{align}
g_2^{tw3} & = \frac{1}{2}\,\sum_a e_a^2
    \biggl(
    \widetilde g_T^{a \star}(x) 
    + \int_x^1\frac{dy}{y} \widehat{g}_T^q(y) 
    \biggr) 
&
g_2^{\text{quark}} &= \frac{1}{2}\,\sum_a e_a^2 
 \frac{\mq}{\Lambda} (h_1^q/x)^\star(x),
&
g_2^{\text{jet}} &= \frac{1}{2}\,\sum_a e_a^2 
\frac{\mj-\mq}{\Lambda} \frac{h_1^q(x)}{x}. 
\end{align} 
These are comapred in Figure~\ref{f:g2contrib} to the $g_2-g_2^{WW}$ function obtained in the very recent JAM15 fit of polarized DIS asymmetries \cite{JAM15}, that includes a large amount of precise data at large $x$ from Jefferson Lab, and simultaneously fits the higher-twist components of in $g_1$ and $g_2$ to the data. For the ``pure twist-3'' contribution, $g_2^{tw3}$, {\it i.e.}, the contribution from quark-gluon-quark matrix elements, we show a model calculation by Braun et al. \cite{Braun-et-al}; for other estimates, see \cite{Other-tw3-calcs}. To estimate the contributions from quark ($g_2^q$) and jet mass ($g_2^{jet}$) effects, that depend on chiral odd quark-quark matrix elements, we use the recent Pavia15 fit of the transversity distribution from Ref.~\cite{Radici:2015mwa}, which is comparable also to other
extractions~\cite{Anselmino:2013vqa,Kang:2015msa}. Furthermore, we choose the values of the mass parameters to be $\mq=5$ MeV and $\mj = 100$ MeV.

@@

\begin{itemize}
\item smaller-$x$: constrains the small-$x$ behavior of transversity.
\end{itemize}
Some ideas to check:
\begin{itemize}
\item JAM13 neutron has almost 0 twist 3, with small positive contribution at small x. Can we use this to highlight teh $g_2^{jet}$ contribution? Or maybe as a cnstrain: if Braun is right then $g_2^{jet}(n) \approx -g_2^{tw3}(n)$. (still, does not help much for the proton).
\item In Jam 13, Fig. 6, it looks like in general the violation of teh BC sum rule is a small-x effect --> constraints on h(x) fits? This cannot really be checked vs. JAM15, that assumes $g_2^(0)$ respects BC. 
\end{itemize}

\begin{figure}[tbh]
\begin{center}
\includegraphics[width=8cm]{g2contrib}
\includegraphics[width=8cm]{g2contribN}
\caption{\label{f:g2contrib} 
Different contributions to the non Wandzura-Wilczek part of the proton (left) and neutron (right) $g_2$ structure function compared to the JAM15 fit of the  $g_2-g_2^{\text{WW}}$ (solid black) \cite{JAM15}. The quark and jet contributions are shown with a dotted red and a dot-dashed green line respectively, with uncertainty bands coming form the Pavia15 fit of the transversity function \cite{Pavia15}. The unceratainty in the choice $m_q=5$ GeV and $M_q=100$ GeV is not shown. The pure twist-3 contribution calculated by Braun et al. \cite{Braun-et-al} is shown as a dashed blue line (no uncertainty estiamte was provided in teh original reference).
}
\end{center}
\end{figure}

It is interesting to consider the moments of the non Wandzura-Wilczek contribution to $g_2$,
\begin{align}
  d_N \equiv (N+1) \int_0^1 x^N \bigg( g_2(x) - g_2^{WW}(x) \bigg) \ .
\end{align}
For a generic function $f$, let us define it's $N$-th moment as $f[N]=\int_0^1 dx\, x^{N} f(x)$. It is then straightforward to verify that $f^*[N] = N/(N+1) \times f[N]$ and  
\begin{align}
  d_N & = (N+1) g_2[N] + N g_1[N] \\
  & = \frac12 \sum_q e_q^2 \bigg( N \tilde g_T^q[N] + \hat g_T^q[N]
    + \frac{(N+1) M_q-m_q}{\Lambda} h_1^q[N] \bigg) \ .
\end{align}

The zero-th moment provides an interestign relationship between the longitudinal and tensor spin structure of the target,
\begin{align}
  \label{eq:BC}
  \int dx\, g_2(x) = \sum_q e_q^2 \frac{\mj-\mq}{\Lambda} \int dx\, \frac{1}{x} h_1^q(x) \ ,
\end{align}
where we used the fact that $\hat g_T^q[0]=0$ identically due to the symmetry properties of the quark-gluon-quark correlators. The sum rule \eqref{eq:BC}, in which the pure twist-3 part does not take part, is a consequence of the Lorentz invariance of QCD interactions, that entails $\int_0^1 dx g_1^a(x) = \int_0^1 g_T^q(x)$. It explicitly displays a contribution from spin-flip processes, that are included in the original derivation by Burkhardt and Cottingham \cite{BC} but do not show up in treatments that only consider free field quark propagators for the struck quark \cite{Jaffe-lectures}. Assuming the Burkhardt-Cottingham sum rule $\int_0^1 dx\, g_2(x) =0$, that is derived at the cross section level (under suitable assumptions on teh high-energy behavior of te hspin-flip amplitude) rather than from an analysis of collinear correlators, as done here, to be strictly valid, we obtain a strong constraint on the transversity function,
\begin{align}
   \int dx\, \frac{1}{x} h_1^q(x) = 0 \ .
\label{eq:ABsumrule}
\end{align}
Interestingly, one can show that this constraint, if valid at any given scale $Q_0$ is conserved through QCD evolution. Even if the BC sum rule is broken either by a $J = 0$ fixed pole with non-polynomial residue \cite{Jaffe-lectures} or explicitly as, \eg, in the quark target model \cite{Metz-Kundu)} -- i.e., if $g_2$ integrates to a finite but non-zero number -- we obtain that $h_1(x)/x$ must be integrable. This entails a bound on the small $x$ behavior of the transversity,
\begin{align}
  h_1^q(x) \propto x^\epsilon \ \ \ \epsilon>0 \ .
\label{eq:ABbound}
\end{align}
This bound will be very useful, \eg, in transversity fits, where the data at small $x$ is, as yet, very limited, and in general for proper extrapolations when calculating moments.

The first moment is the first in which a contribution from the pure twist-3 part of $g_2$ appears:
\begin{align}
  d_1 & = \frac12 \sum_q e_q^2 \bigg( 2 \tilde g_T^q[1] + \hat g_T^q[1]
    + \frac{2M_q-m_q}{\Lambda} h_1^q[1] \bigg)
\end{align}
where $h_1^q[1] = \int_0^1 dx h_1^q(x)$ is the contribution of a quark $q$ to the tensor charge. 
The third moment is also interesting because the pure twist-3 part can be related to quark-gluon-quark correlators, see \cite{Jaffe-lectures}, and interpreted as as the average color force experienced by the struck quark as it exits the nucleon \cite{M.Burkardt}:
\begin{align}
  d_2 & = \frac12 \sum_q e_q^2 \bigg( 3 \tilde g_T^q[2] + \hat g_T^q[2]
    + \frac{3M_q-m_q}{\Lambda} h_1^q[2] \bigg)
\end{align}
In both of these cases, the transversity contribution is a background to the extraction of the pure twist-3 piece. Fortunately, it is a quantity that can be extracted from the lattice \cite{Bhattacharya:2016zcn} or fitted \cite{Pavia15, others, reviews?}. Furthermore, the new sum rule \eqref{eq:ABsumrule} and the bound \eqref{eq:ABbound} promise to improve future transversity fits. What is less obvious is how to calculate $M_q-m_q$ from first principles, since this is related to the spectral function of the quark propagator. We will, however, briefly discuss perspectives on how to measure it. Therefore the pure twist-3 part can, in principle, be properly isolated.

\begin{figure}[tbh]
  \centering
  \parbox[b]{8cm}{\centering
  \includegraphics
      [width=7cm,clip=true]
      {epl_emn_h_X.eps}
  }
  \parbox[b]{8cm}{\vskip-0.5cm\centering
  \includegraphics
      [width=7cm,clip=true]
      {epl_emn_h_h_X.eps}
  }
  \caption{\small
	Single hadron {\it (left)} and double hadron {\it (right)}
	production in $e^+ e^-$ collisions at LO with jet and
	fragmentation correlators.
  }
  \label{fig:epl_emn_h}
\end{figure}

A promising avenue to experimentally access jet functions is, however, through inclusive single hadron production, $e^+ e^- \to h X$, and inclusive dihadron 
production from the same hemisphere, $e^+ e^- \to h h X$, see 
Fig.~\ref{fig:epl_emn_h}.
In single-hadron production, the fragmentation functions $D_h$
play the role of PDFs in DIS, and couple to the jet functions
in an analogous way.
In double hadron production the enlarged number of Dirac structures
of the dihadron fragmentation correlator $D_{2h}$ allows one to access
the jet function in novel ways, and in particular to isolate the
contribution from the helicity-flip $J_0$ term.
Studying and classifying all the possibilities offered by single and
double hadron production will open up a rich phenom, which will in turn
be needed to extract pure twist-3 matrix elements from the $g_2$ structure function, and more in general to perform precise jet mass corrections in DIS.
